---
title: "QUANTITATIVE Management Modelling Assignment 2"
author: "SUMIT DUTT MISHRA"
date: "04/10/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
###Installing the library
```{r}
library(lpSolveAPI)
```
###Setting the work directory
```{r}
setwd("~/Desktop/SEMESTER 2/QUANT MANAGEMENT")
```

### Creating a linear programming object with 0 constraints and 9 decision variables
```{r}
lpmodel1 <- make.lp(0, 9)
lpmodel1
```
### Creating the objective function. since we need to maximize profit, change the sense to max.
```{r}
set.objfn(lpmodel1, c(420, 360, 300, 420, 360, 300, 420, 360, 300))
```
### As we need to maximize profit, we need to change the sense to maximum.
```{r}
lp.control(lpmodel1,sense='max')
```
# Adding the constraints
```{r}
add.constraint(lpmodel1, c(1, 1, 1, 0, 0, 0, 0, 0, 0), "<=", 750)
add.constraint(lpmodel1, c(0, 0, 0, 1, 1, 1, 0, 0, 0), "<=", 900)
add.constraint(lpmodel1, c(0, 0, 0, 0, 0, 0,1, 1, 1), "<=", 450)
add.constraint(lpmodel1, c(20, 15, 12, 0, 0, 0, 0, 0, 0), "<=", 13000)
add.constraint(lpmodel1, c(0, 0, 0, 20, 15, 12, 0, 0, 0), "<=", 12000)
add.constraint(lpmodel1, c(0, 0, 0, 0, 0, 0, 20, 15, 12), "<=", 5000)
add.constraint(lpmodel1, c(1, 1, 1, 0, 0, 0, 0, 0, 0), "<=", 900)
add.constraint(lpmodel1, c(0, 0, 0, 1, 1, 1, 0, 0, 0), "<=", 1200)
add.constraint(lpmodel1, c(0, 0, 0, 0, 0, 0, 1, 1, 1), "<=", 750)
add.constraint(lpmodel1, c(6, 6, 6, -5, -5, -5, 0, 0, 0), "=", 0)
add.constraint(lpmodel1, c( 3, 3, 3, 0, 0, 0, -5, -5, -5), "=", 0)
```
```{r}
set.bounds(lpmodel1, lower = c(0, 0, 0, 0, 0, 0, 0, 0, 0), columns = c(1, 2,3,4,5,6,7,8,9))
```
# Setting variable names and name the constraints for identifying the variables and constraints
```{r}
Rows <- c("CCon1", "CCon2", "CCon3", "SCon1", "SCon2", "SCon3", "S1Con1", "S1Con2", "S1Con3", "%C1", "%C2")

Columns <- c("A1Large", "A1Medium", "A1Small", "A2Large", "A2Medium", "A2Small", "A3Large", "A3Medium", "A3Small")

dimnames(lpmodel1) <- list(Rows, Columns)
```
```{r}
lpmodel1
```
```{r}
write.lp(lpmodel1, filename = "Quantsassignment2.lp", type = "lp")
```
```{r}
solve(lpmodel1)
```
```{r}
get.objective(lpmodel1)
get.variables(lpmodel1)
```


 



